ABM and CM Reference Notes

### 2018-07-03 paper/old_drafts/draft_v5.tex
finally on git

\usepackage{tikz}
\tikzset{
  int/.style={circle, draw, fill=blue!20, minimum size=3em},
  init/.style={pin distance=1.2cm,pin edge={loop,thin,black}}
}
\usetikzlibrary{arrows}

@@

>>>>

\usepackage{tikz}
\tikzset{
  int/.style={circle, draw, fill=blue!20, minimum size=3em},
  init/.style={pin distance=1.2cm,pin edge={loop,thin,black}}
}
\usetikzlibrary{arrows,automata}

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[node distance=3cm,auto,>=latex',every node/.append style={align=center}]
  \node [int,  fill = white!70!blue] (s)              {$S$};
  \node[int, fill = white!70!blue] (m) [left of=s] {$M$};
  \node [int,  fill = white!70!blue] (e) [right of=s]             {$E$};
  \node [int,  fill = white!70!blue]           (i) [right of=e] {$I$};
  \node [int,  fill = white!70!blue] (r) [right of=i] {$R$};
  \path[->, auto=false] (s) edge node {} (e)
  (e) edge node {} (i)
  (i) edge node {} (r)
  (m) edge node {} (s)
  ++ (0,2) edge node {} (m)
  (s) ++ (0,2) edge node {} (s);
  \path[->]   (m) edge node {}  ++ (0,-2);
  \path[->]   (s) edge node {}  ++ (0,-2);
  \path[->]   (e) edge node {}  ++ (0,-2);
  \path[->]   (i) edge node {}  ++ (0,-2);
  \path[->]   (r) edge node {}  ++ (0,-2);
\end{tikzpicture}
\caption{Depiction of a MSEIR model with birth and death rates.  $M$ - passive immunity from mother; $S$ - susceptible; $E$- exposed, latent; $I$- infected; $R$ - recovered.  An arrow out of the system indicates death and an arrow into the system indicates birth.}\label{fig::mseir}
\end{figure}

This compartment model approach includes not only the exposed, latent compartment $E$ but additionally the compartment $M$ which stands for passive immunity inherited from the mother.  \cite{hethcote2000} describe the model with the following set of ODES that include birth rate $b$ and death rate $d$, respectively (reparametrized to match our notation),
\begin{align*}
  \frac{dM}{dt} &= b(N-X) - (\delta + d) M \\
  \frac{dX}{dt} &= bX + \delta M - \frac{\beta XY}{N} - dX\\
  \frac{dE}{dt} &= \frac{\beta XY}{N} - (\epsilon + d) E\\ 
  \frac{dY}{dt} &= \epsilon E - (\gamma + d) Y \\
  \frac{dZ}{dt} &= \gamma Y - dZ \\
  \frac{dN}{dt} &= (b-d)N,
\end{align*}
where $\delta$ is the rate of passive, immune infants transitioning to susceptible indnividuals, $\beta$ is the rate of infection, $\epsilon$ is the rate of of infectious individuals becoming infected, and $\gamma$ is the rate of recovery.  The reproduction number is then,
\begin{align}\label{eq:r0-mseir}
\rr &= \frac{ \beta \epsilon}{ (\gamma + b)(\epsilon + b)}.
\end{align}
\cite{hethcote2000} note that this calculation of $\rr$ may be strictly derived through interpretation of the definition, as ``$\rr$ is the product of the contact rate $\beta$ per unit time, the average infectious period adjusted for population growth of $\frac{1}{\gamma + b}$ and the fraction $\frac{\epsilon}{\epsilon + b}$ of exposed people surviving the latent class $E$.''  They note that this model is well suited for diseases such as measles, rubella, or mumps where the mother may pass some antibodies to her newborn.  This expression may also be derived using the next generation operator described in Section \ref{sec:ngm}.

Again, this is simply a model for transmission of a disease and does not specify how $\rr$ is to be estimated once the model is written down.  Method such as least squares and MLE are common ways to estimate the parameters in this model and hence $\rr$.  When the birth rate $b=0$, note that $\rr$ reduces to the derived expression for both the SIR and SEIR models without birth and death rates, $\frac{\beta}{\gamma}$.

### 2018-07-03 references/refs.tex
finally on git

\message{ !name(refs.tex)}\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{scalerel}
\usepackage{graphicx}% http://ctan.org/pkg/graphicx
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

@@

\begin{document}

\message{ !name(refs.tex) !offset(-3) }

\bibliographystyle{plain}%Choose a bibliograhpic style

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Variance in System Dynamics and Agent Based Modelling Using the SIR Model of Infectious Disease

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Dynamically Modeling SARS and Other Newly Emerging Respiratory Illnesses: Past, Present, and Future

@@

\textbf{Notes:} See r0.tex.  Read 6/16/2016
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Comparing methods for estimating R0 from the size distribution of subcritical transimission chains

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Theory versus Data:  How to Calculate $R_0$?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  On the definition and the computation of the basic reproduction ratio R0 in models for infectious diseases in heterogeneous populations

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  The estimation of the basic reproduction number for infectious diseases

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  On the True Rate of Natural Increase

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} The Asymptotic Distributions of Kernel Estimators of the Mode

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Agent-Based Computational Models and Generative Social Science

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Detail in network models of epidemiology: are we there yet?

@@

disease is stochastic enough (p454)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Factors That Make an Infectious Disease Outbreak Controllable

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  A likelihood‐based method for real‐time estimation of the serial interval and reproductive number of an epidemic

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Introduction to ``The First Draft Report on the EDVAC'' by John von Neumann

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Pattern-Oriented Modeling of Agent Based Complex Systems

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Exact analytical solutions of the SIR Model

\textbf{Author:}  Tiberiu Harko, Francisco Lobo, MK Mak

@@

\textbf{Notes:}  See write up in ABM
\\
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  A Brief History of R0 and a Recipe for its Calculation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  The Concept of R0 in Epidemic Theory

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Perspectives on the basic reproduction ratio

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} The Mathematics of Infectious Diseases

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  A Contribution to the Mathematical Theory of Epidemics

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Solutions of Ordinary Differential Equations as Limits of Pure Jump Markov Processes

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Sex ratio features of two-group SIR model for asymmetrie transmission of heterosexual disease

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} The analysis of equilibirum in malaria

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} The analysis of equilibrium in malaria

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  19 Dubious ways to compute the Exponential of a Matrix, 25 Years Later

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Methods and Techniques of Complex Systems Science:  An Overview

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Revisiting the Basic Reproductive Number for Malaria and Its Implications for Malaria Control

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  A note on generation times in epidemic models

@@

\textbf{Citation:}\cite{Svensson2007}

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Epidemic Modelling:  An Introduction

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Infectious Diseases of Humans

@@

\textbf{Ch. 7} Dynamic aspects of eradication and control

k \textbf{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:}  Agent-based modeling: Methods and techniques for simulating human systems

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Growing Artificial Socities:  Social Science from the Bottom Up (Complex Adaptive Systems) 1st Edition

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\textbf{Title:}  Complex Adaptive Systems:  An Introduction to Computational Models of Social Life

@@

\textbf{Notes:}
\\
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Advanced Data Analysis from an Elementary Point of View

@@

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Notes on $R_0$

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Title:} Agent-Based Modeling

@@

\message{ !name(refs.tex) !offset(-936) }

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{scalerel}
\usepackage{graphicx}% http://ctan.org/pkg/graphicx
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

@@

\begin{document}
\bibliographystyle{plain}%Choose a bibliograhpic style

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} An Examination of the Reed-Frost Theory of Epidemics

\textbf{Author:}  Helen Abbey

\textbf{Citation:} \cite{abbey1952}

\textbf{Link:} \url{abbey1952.pdf}

\textbf{Major themes:}  Reed Frost theory of epidemics, r0

\textbf{Intro:}
\begin{itemize}
\item ``If certain combinations of assumptions give a better fit [to the model] than others, the simplest assumptions which give a good fit provide working leads for further study of the actual relationships which have been approximated by the model'' (p201)
\item ``The estimates of the parameters of the model may be useful in comparing different diseases or the same disease under different environmental conditions'' (p201)
\item Reed and Frost adapted a model proposed by Soper (1927), the Reed-Frost model
\item ``Soper had postulated a community in which all individuals had equal susceptibility to a disease, equal capacity to transmit it, and the power of passing out of observation when the transmitting period was over'' (p202)
\item law of mass action is ``assumed to apply to the transmission of the disease'' (p202)
\item model adapated so susceptible person can only get disease once from infected people
\item assumptions of Reed-Frost (p202)
  \begin{itemize}
  \item spread through a particular kind of contact and ``in no other way''
  \item person infected will become immune after time period
  \item ``Each individual has a fixed probability of coming into adequate contact with any other specified individual in the group...andthis probability is the same for every member of the group'' (homogeneity (p202)
  \item this is a closed system, during which the model is constant
  \item ``infective period is short relative to the incubation period'' (p203)
  \end{itemize}
\item ``$p$ is the probability of contact between any two specified individuals'' (p202)
\item contact == infecting a new person.  $p$ is dependent on the susceptiblity/resistance of person, infectivity of disease, ``length of exposure and size of dose necessary to produce the disease, as well as environmental conditions necessary'' (p202-203)
\item  The model of Soper (verbatim)  (p203)
  \begin{itemize}
  \item $p$ contact probability
  \item  $q = 1-p$
  \item $C_t$ is the number of cases produced at time $t$
  \item $q^{C_t}$ is the probability that the specified individual will not have contact with any of the $C_t$ cases
  \item $1-q^{C_t}$ is the probablity he will have contact with at least one
  \item$S_t$ number of susceptibles at time $t$
  \item $C_{t+1} = S_t (1 - q^{C_t})$ (expected number of cases)
  \end{itemize}
\item Reed-Frost have a probabilistic model where infection is a binomial distribution (p204-205)
  \item assumptions of diseases to fit this model (206) 
  \item measles, German measles and chicken pox fit these failry well
  \item Scarlet fever, polio, diphtheria, mumps, and whooping cough do not fit this model well
  \item ``The method which is used for estimating a single contact rate for the entire epidemic if the ``method of maximum likelihood" (p210)
  \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Variance in System Dynamics and Agent Based Modelling Using the SIR Model of Infectious Disease

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Dynamically Modeling SARS and Other Newly Emerging Respiratory Illnesses: Past, Present, and Future

@@

\textbf{Notes:} See r0.tex.  Read 6/16/2016\\
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Modeling the emergence of the'hot zones': tuberculosis and the amplification dynamics of drug resistance

\textbf{Author:}  blower and chou

\textbf{Citation:} \cite{blower2004}

\textbf{Link:} \url{blower2004.pdf}

\textbf{Major themes:} tuberculosis, r0, amplifier model

\textbf{Notes:} 
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Comparing methods for estimating R0 from the size distribution of subcritical transimission chains

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Theory versus Data:  How to Calculate $R_0$?

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Dynamically Modeling SARS and Other Newly Emerging Respiratory Illnesses: Past, Present, and Future

\textbf{Author:}  Cintron-Arias et al

\textbf{Citation:} \cite{cintronarias2009}

\textbf{Link:} \url{cintronarias2009.pdf}

\textbf{Major themes:}  r0, least squares, asymptotic theories for mean and variance.

\textbf{Notes:} 
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Pharamacokinetic-Pharmacodynamic Modelling:  History and Perspectives

\textbf{Author:} Csajka and Verotta

\textbf{Citation:}\cite{csajka2006}

\textbf{Link:} \url{csajka2006.pdf}

\textbf{Major themes:} Compartment Models

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  On the definition and the computation of the basic reproduction ratio R0 in models for infectious diseases in heterogeneous populations

@@

\textbf{Notes:}  See r0.tex.  Read 6/20/16
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  The estimation of the basic reproduction number for infectious diseases

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  On the True Rate of Natural Increase

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} The Asymptotic Distributions of Kernel Estimators of the Mode

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} The Asymptotic Distributions of Kernel Estimators of the Mode

\textbf{Citation:} \cite{eddy1980}

\textbf{Link:} \url{eddy1980.pdf}

\textbf{Major themes:}  modes, convergence, normal distribution

\textbf{Read:}
\\
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Agent-Based Computational Models and Generative Social Science

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Detail in network models of epidemiology: are we there yet?

@@

disease is stochastic enough (p454)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Factors That Make an Infectious Disease Outbreak Controllable

@@

\textbf{Notes:}  See r0.tex.  Read 6/21/16
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  A likelihood‐based method for real‐time estimation of the serial interval and reproductive number of an epidemic

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Introduction to ``The First Draft Report on the EDVAC'' by John von Neumann

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Pattern-Oriented Modeling of Agent Based Complex Systems

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Modeling of epidemic spreading with white Gaussian noise

\textbf{Author:} Gu, Gao, and Li

\textbf{Citation:}\cite{gu2011}

\textbf{Link:} \url{gu2011.pdf}

\textbf{Major themes:}  Adding noise to SIR

\textbf{Read: }
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Exact analytical solutions of the Susceptible-Infected-Recovered (SIR) epidemic model and of the SIR model with equal death and birth rates

\textbf{Author:}  Harko

@@

\textbf{Notes:}  See write up in ABM

\textbf{Read:}
\\
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  A Brief History of R0 and a Recipe for its Calculation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  The Concept of R0 in Epidemic Theory

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Perspectives on the basic reproduction ratio

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} The Mathematics of Infectious Diseases

@@

\textbf{Notes:} See r0.tex
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Effects of quarantine in six endemic models for infectious diseases

\textbf{Author:}  Hethcote 2002

\textbf{Link:} \url{hethcote2002.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Transmission Dynamics and Control of Severe Acute Respiratory Syndrome

\textbf{Author:} Lipsitch et al 2003

\textbf{Citation:}\cite{lipsitch2003}

\textbf{Link:} \url{lipsitch2003.pdf}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  A Contribution to the Mathematical Theory of Epidemics

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Solutions of Ordinary Differential Equations as Limits of Pure Jump Markov Processes

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Sex ratio features of two-group SIR model for asymmetrie transmission of heterosexual disease

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} The analysis of equilibirum in malaria

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} The analysis of equilibrium in malaria

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  19 Dubious ways to compute the Exponential of a Matrix, 25 Years Later

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Methods and Techniques of Complex Systems Science:  An Overview

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Revisiting the Basic Reproductive Number for Malaria and Its Implications for Malaria Control

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  A note on generation times in epidemic models

@@

\textbf{Citation:}\cite{Svensson2007}\\

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} A methodology to match distributions of both household and person attributes in the generation of synthetic populations

\textbf{Author:}  Ye et al

\textbf{Citation:} \cite{ye2009methodology}

\textbf{Link:} \url{ye2009methodology.pdf}

\textbf{Major themes:}  IPU

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Random Fields and Geometry

\textbf{Author:}  Adler and Taylor

\textbf{Citation:} \cite{adler2007}

\textbf{Link:} \url{adler2007.pdf}

\textbf{Major themes:}  Gaussian processes, smoothness conditions for covariance matrix

\textbf{Notes:}
\textbf{Ch. 1}

\vskip .2cm
\hrule
\vskip .2cm
%%%%%%%%%%%%%%%%%%%%%%

\textbf{Title:} Epidemic Modelling:  An Introduction

@@

\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Infectious Diseases of Humans

@@

\textbf{Ch. 7} Dynamic aspects of eradication and control
\begin{itemize}
\item ``the time steps used in approximating partial differential equations (7.6)-(7.9) must be chosen carefully'' (p153)
\end{itemize}

\textbf{Beyond the basic model: empirical evidence for inhomogeneous mixing}
\begin{itemize}
\item d
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Agent-based modeling: Methods and techniques for simulating human systems

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Growing Artificial Socities:  Social Science from the Bottom Up (Complex Adaptive Systems) 1st Edition

@@

\textbf{Notes:}
\\
%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Wiley series in mathematical and computational biology

\textbf{Author:}  Diekmann and Heesterbeek 2000

\textbf{Citation:} \cite{diekmann2000}

\textbf{Major themes:} r0

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Statistical Analysis of Stationary Time Series

\textbf{Author:}  Grenander and Rosenblatt

\textbf{Citation:} \cite{grenander1957}

\textbf{Major themes:}  time series, gaussian processes

\textbf{Notes:} See scans.  Due Jan 17, 2017

\textbf{Preface}
\begin{itemize}
\item k
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 5
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:}  Complex Adaptive Systems:  An Introduction to Computational Models of Social Life

@@

\textbf{Notes:}
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Gaussian Processes for Machine Learning

\textbf{Author:}  Rasmussen and Williams 2006

\textbf{Citation:} \cite{rasmussen2006}

\textbf{Link:} \url{rasmussen2006.pdf}

\textbf{Major themes:}  gaussian processes, covariance

\textbf{Ch. 4 Covariance Functions}

\begin{itemize}
  \item ``The notion of \textit{similarity} between data points is crucial; it is a basic assumption that points with inputs \textbf{x} which are close are likely to have similar target values $y$'' (p79) 
  \item ``Under the Gaussian process view it is the covariance function that defines nearness or similarity'' (p79)
  \item ``A \textit{stationary} covariance function is a function of $\mathbf{x} - \mathbf{x}^\prime$...If further the covariance is a function of $|\mathbf{x}-\mathbf{x}^\prime|$ then it is called \textit{isotropic}...These are also known as \textit{radial basis functions} (RBFs)'' (p79-80)
  \item ``If a covariance function depends only on $\mathbf{x}$ and $\mathbf{x}^\prime$ through $\mathbf{x} \cdot \mathbf{x}^\prime$ we call it a \textit{dot product} covariance function...Dot product covariance functions are invariant to a rotation of the coordinates about the origin, but not translations'' (p80)
  \item ``A general name for a function $k$ of two arguments mapping a pair of inputs $\mathbf{x}, \mathbf{x}^\prime \in \mathcal{X}$ into $\mathbb{R}$ is a \textit{kernel}...clearly covariance functions must be symmetric'' (p80)
  \item ``A \textit{kernel} is said to be positive semidefinite if $\int k(\mathbf{x}, \mathbf{x}^\prime)f(\mathbf{x})f(\mathbf{x}^\prime) d\mu(\mathbf{x}) d\mu(\mathbf{x}^\prime) \ge 0,$ for all $f \in L_2(\mathcal{X}, \mu)$.'' (p80)
  \item ``Let $\mathbf{x}_1, \mathbf{x}_2, \dots$ be a sequence of points and $\mathbf{x}_*$ be a fixed point in $\mathbb{R}^D$ such that $|\mathbf{x}_k - \mathbf{x}*| \to 0$ as $k \to \infty$.  Then a process $f(\mathbf{x})$ is continuous in mean square at $\mathbf{x}_*$ if $E[|f(\mathbf{x}_k) - f(\mathbf{x}_*)|^2] \to 0$ as $k \to \infty$.  If this holds for all $\mathbf{x}_*\in A$ where $A$ is a subset of $\mathbb{R}^D$ then $f(\mathbf{x})$ is said to be continuous in mean square (MS) over $A$'' (p81)
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Epidemic MOdels: Their Structure and RElation to Data

\textbf{Author:}  Mollison 1995

\textbf{Citation:} \cite{mollison1995}

\textbf{Major themes:} r0, epidemic models

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Advanced Data Analysis from an Elementary Point of View

@@

\textbf{Notes:}
\\
%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm

\textbf{Title:} Notes on $R_0$

@@

%%%%%%%%%%%%%%%%%%%%%%
\vskip .2cm
\hrule
\vskip .2cm
\textbf{Title:} Agent-Based Modeling

@@
